Gafo-cc visuals

### 2023-05-03 analysis/gafo-cc-data-processing.Rmd
move to cluster

@@

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/leipzig/", pattern = "*.json",recursive = T)

@@

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  #read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/", sheet = 1)
  read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(!is.na(ageinyears),
         status == "keep")
```

@@

@@

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(location = community,
         community = "akure")
```

@@

```{r read_data}
# get all .json files
files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_zambia <- tibble()
for (f in files) {
  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

@@

@@

```{r demographics}
raw_demographics_zambia <- bind_rows(
  read_ods("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/gafo-cc-sambia-participants.ods", sheet = 1)
  )

tidy_demographics_zambia <- raw_demographics_zambia %>% 
  filter(community!= "leipzig")%>%
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_zambia <- tidy_demographics_zambia%>%
  left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "chimfunshi")
```

```{r}
data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(screen == "touchscreen", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)
```

@@

data <- bind_rows(
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_zambia,
  data_stanford
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

data%>%
  group_by(community)%>%
  summarise(n= n_distinct(subjid))

```{r}
data%>%
  filter(community == "leipzig")%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(screen, age_group)%>%
  summarise(n = n_distinct(subjid))
```

```{r}
write_csv(data,"../data/gafo-cc-clean-data.csv")
```

>>>>

```{r}
data_namibia%>%
  filter(community == "windhoek")%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

data_namibia%>%
  filter(community == "windhoek")%>%
  group_by(ageinyears)%>%
  summarise(n= n_distinct(subjid))%>%
  ggplot(aes(x = ageinyears, y = ""))+
  geom_count(alpha = .5)+
  xlim(2.5, 8)+
  theme_bw()
```

@@

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/leipzig/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)

@@

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  #read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(status == "keep")
```

@@

data_leipzig%>%
  #group_by(subjid)%>%
  summarise(n = n_distinct(subjid))

data_leipzig%>%
  mutate(age_group = substr(ageinyears, 1, 1))%>%
  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
  na.omit()%>%
  group_by(age_group, sex)%>%
  summarise(n = n_distinct(subjid))

data_leipzig%>%
  mutate(age_group = substr(ageinyears, 1, 1))%>%
  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
  na.omit()%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))
```

@@

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(location = community,
         community = "akure")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/zambia/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_zambia <- tibble()
for (f in files) {
  jf <- paste("../../raw_data/gafo-cc/zambia/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = paste0("z", subjID),
  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r demographics}
raw_demographics_zambia <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/zambia/Gafo_cc_Zambia_April23_Final.xlsx", sheet = 1)
  )

tidy_demographics_zambia <- raw_demographics_zambia %>% 
  filter(community!= "leipzig")%>%
  mutate(
    #test_date = as.Date(test_date, format = "%d/%m/%Y"),
    #birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    id = paste0("z", id),
    screen = ifelse(screen == "yes", 1, 0),
    touchscreen = ifelse(touchscreen == "yes", 1, 0)
  )  %>%
  filter(status == "keep")%>%
  select(-c(test_date, birth_date, comment, Age, consent_signed, Nr, status))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_zambia <- tidy_demographics_zambia%>%
  left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "chimfunshi")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

```{r}
data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(touchscreen == "yes", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)%>%
  distinct(subjid, trialnr, .keep_all = T)
```

```{r}
data_stanford%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

# Plymouth

```{r}
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-uk/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/plymouth/")
```

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/plymouth/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)

# convert json files to tibbles
raw_data_plymouth <- tibble()
for (f in files) {
  jf <- paste("../../raw_data/gafo-cc/plymouth/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_plymouth <- bind_rows(raw_data_plymouth, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_plymouth <- raw_data_plymouth %>%

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID =as.factor(subjID))%>%select(-touchScreen)%>%
  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

```{r}
tidy_data_plymouth%>%
  filter(trialType == "test")%>%
  group_by(subjID)%>%
  summarise(n = n())

tidy_data_plymouth%>%
  filter(trialType == "test")%>%
  summarise(n = n_distinct(subjID))
```

```{r demographics}
raw_demographics_plymouth <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information.xlsx", sheet = 1)
  )

test_date_plymouth <- tidy_data_plymouth%>%
  select(subjID, timestamp)%>%
  mutate(test_date = as.Date(substr(timestamp, 1,10),format = "%Y-%m-%d"))%>%
  select(-timestamp)%>%
  rename_all(tolower)

tidy_demographics_plymouth <- raw_demographics_plymouth %>% 
  select(-test_date)%>%
  left_join(test_date_plymouth)%>%
  mutate(
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    younger_children = ifelse(younger_children == "N/A", NA, younger_children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))
```
```{r}
data_plymouth <- tidy_demographics_plymouth%>%
  left_join(tidy_data_plymouth%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_plymouth%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

data_plymouth%>%
  group_by(subjid)%>%
  summarise(n())

# Mexico

```{r read_data}
# get all .json files
files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_mex <- tibble()
for (f in files) {
  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_mex <- bind_rows(raw_data_mex, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_mex <- raw_data_mex %>%

@@

```{r}
tidy_data_mex%>%
  summarise(n = n_distinct(subjID))
```

```{r demographics}
raw_demographics_mex <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/participants.xlsx", sheet = 1)
  )%>%
  filter(!is.na(lastname))%>%
  mutate(birth_date = ifelse(birth_date == 29042017, 20170429, birth_date))

tidy_demographics_mex <- raw_demographics_mex %>% 
  mutate(

    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(name, lastname, test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))

```{r}
data_mex <- tidy_demographics_mex%>%
  left_join(tidy_data_mex%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "mexico")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_mex%>%summarise(n = n_distinct(subjid))
```

# China

```{r}
system("rsync -zaP ccp-odcJ:/srv/ccp-odc/gafo-china/data/ ~/Work/Local/QuantEx/Gafo/raw_data/gafo-cc/china/")
```

```{r read_data}
# get all .json files
files <- list.files("../../raw_data/gafo-cc/china/", pattern = "*.json",recursive = T)%>% str_subset(pattern = "gafo--", negate = T)

# convert json files to tibbles
raw_data_china <- tibble()
for (f in files) {
  jf <- paste("../../raw_data/gafo-cc/china/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_china <- bind_rows(raw_data_china, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_china <- raw_data_china %>%

  # convert all character vectors into factors

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = ifelse(grepl("2023-04-13T03:1", timestamp), "china075", subjID),
         subjID = ifelse(grepl("2023-04-13T07:0", timestamp), "china077", subjID))%>%
  select(-touchScreen)%>%
  distinct(subjID, trialNr, .keep_all = T)%>%
   mutate_if(is.character, as.factor)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

#unique(tidy_data_leipzig$subjID)

tidy_data_china%>%
  filter(subjID == "china077")

```{r demographics}
raw_demographics_china <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/china/gafo-cc-participants_China_0421.xlsx", sheet = 1, 
            col_types = c("text", "text", "text", "skip", "skip", "skip", "date", "date", "numeric", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))
  )%>%
  filter(!row_number() == 1)

tidy_demographics_china <- raw_demographics_china %>% 
  mutate(
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25)
  )  %>%
  select(-c(test_date, birth_date, comment))%>%
  filter(status == "included", 
         !is.na(ageinyears))%>%
  select(-status)%>%
  rename(subjid = id)

tidy_demographics_china%>%
  arrange(ageinyears)
```

```{r}
data_china <- tidy_demographics_china%>%
  left_join(tidy_data_china%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_china%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

data_china%>%
  group_by(subjid)%>%
  summarise(n())

@@

data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")%>%
  mutate(age_group = substr(ageinyears, 1,1))

write_csv(data,"../data/gafo-cc-clean-data.csv")

data%>%
  filter(touchscreen == 2)
```

```{r}
data_plymouth%>%
  summarise(n= n_distinct(subjid))

data%>%
  group_by(community)%>%
  summarise(n= n_distinct(subjid))
```

### 2023-05-03 analysis/gafo-cc-visuals.Rmd
move to cluster

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(community = recode(community,
                            akure = "akure (nigeria)",
                            leipzig = "leipzig (germany)",
                            `hai||om` = "hai||om (namibia)",
                            khwe = "khwe (namibia)",
                            windhoek = "windhoek (namibia)",
                            stanford = "stanford (usa)",
                            chimfunshi = "chimfunshi (sambia)"))
```

@@

data%>%
  summarise(n= n_distinct(subjid))
```

```{r}
data%>%
  filter(community != "chimfunshi (sambia)")%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(alpha = .25)+
  geom_smooth(method = "glm")+
  scale_color_colorblind(name = "Community")+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "right")

@@

```{r}
ptp<- data%>%
  filter(community != "chimfunshi (sambia)")%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
  scale_color_colorblind(name = "Community")+
  ylim(0,1000)+
  theme_minimal()
```

@@

```{r}
pred <- data%>%
  group_by(community)%>%
  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)), 
         household = scale(household), 
         children = scale(children),
         younger_children = scale(younger_children))%>%
  group_by(subjid, household, children, younger_children)%>%
  summarise(mean= mean(clickdistfromtargetcenterx))%>%
  pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
  group_by(predictor)%>%
  mutate(value = scale(value))

>>>>

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(community = recode(community,
                            akure = "akure (nigeria)",
                            leipzig = "leipzig (germany)",
                            `hai||om` = "hai||om (namibia)",
                            khwe = "khwe (namibia)",
                            windhoek = "windhoek (namibia)",
                            stanford = "stanford (usa)",
                            chimfunshi = "chimfunshi (sambia)",
                            mexico = "ocuilan (mexico)",
                            plymouth = "plymouth (uk)",
                            beijing = "beijing (china)"))
```

@@

data%>%
  summarise(n= n_distinct(subjid))

data%>%
  group_by(community, age_group)%>%
  summarise(n = n_distinct(subjid))
```

```{r}
data%>%
  #filter(community != "chimfunshi (sambia)")%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(alpha = .25)+
  geom_smooth(method = "lm")+
  scale_color_ptol(name = "Community")+
  ylim(0,1000)+
  #facet_wrap(~community)+
  labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "right")

@@

```{r}
data%>%
  distinct(targetposition, targetcentralityx)%>%
  expand_grid(random_click = runif(10000, min = 0, max = 1920))%>%
  mutate(dist = abs(targetcentralityx - random_click))%>%
  group_by(targetposition)%>%
  summarise(random = mean(dist))

```{r}
ptp<- data%>%
  #filter(community != "chimfunshi (sambia)")%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  #group_by(community, targetposition, age_group)%>%
  group_by(community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

alt1 <- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(targetposition)%>%
  summarise(center = mean(targetcentralityx))%>%
  mutate(group = "group")%>%
  ungroup()

alt2 <- data%>%
  distinct(targetposition, targetcentralityx)%>%
  expand_grid(random_click = runif(10000, min = 0, max = 1920))%>%
  mutate(dist = abs(targetcentralityx - random_click))%>%
  group_by(targetposition)%>%
  summarise(random = mean(dist))%>%
  mutate(group = "group")

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_line(data = alt1, aes(x = targetposition, y = center, group = group), lty = 3, alpha = 0.75, col = "black")+
  geom_line(data = alt2, aes(x = targetposition, y = random, group = group), lty = 3, alpha = 0.75,  col = "black")+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Target position (binned)", y = "Imprecision (average click distance from target)")+
  scale_color_ptol(name = "Community")+
  #facet_grid(~age_group)+
  ylim(0,1000)+
  theme_minimal()
```

@@

```{r}
pred <- data%>%
  group_by(community)%>%
  mutate(clickdistfromtargetcenterx = scale(abs(clickdistfromtargetcenterx)), 
         household = scale(household), 
         children = scale(children),
         younger_children = scale(younger_children))%>%
  group_by(subjid,community, household, children, younger_children)%>%
  summarise(mean= mean(clickdistfromtargetcenterx))%>%
  pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
  group_by(predictor)%>%
  mutate(value = scale(value))
